Manuscript draft

### 2018-11-28 r/Manuscript draft.Rmd
11/27 more

---
title: "Status Nov. 2018"
author: "Molly Wilson"
date: "Dec. 2018"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
---

@@

sum_id_pca <- read.csv(here("data","sum_id_pca.csv"), stringsAsFactors=F) %>%
  select(-X) 
sum_ssp_pca <- read.csv(here("data","sum_ssp_pca.csv"), stringsAsFactors=F) %>%
  select(-X) 
```

@@

## Data collection
* Sites (map), timeline
* Fish and benthic community data
* Behavioral data:
    - Species: *Sparisoma viride* and *Scarus vetula*, initial and terminal phase greater than 15cm
    - 2 minute follows, calibration period, outside of previously established FID
    - Recording time budgets as well as bite rates during grazing forays (define)
    - Discarded data of incomplete follows or where fish were visably disturbed/fled
    - Timing of data collection distributed throughout day

@@

## Differences in feeding behaviors among islands

```{r, echo=F, message=F, warning=F}
knitr::include_graphics(here("figs/vp_fr.png"))
knitr::include_graphics(here("figs/vp_br.png"))
knitr::include_graphics(here("figs/vp_gfrac.png"))
```

## Impacts on total grazing pressure

Here I take calculate the predicted reef area grazed per hour of a given scarid (*S. viride* and *S. vetula*) population. I calculate individual predicted grazing impact based on observed and previously published length - feeding rate relationships and multiply these based on published length - bite size relationships for each species.

```{r, echo=F, message=F, warning=F}
knitr::include_graphics(here("figs/sp_fr_length.png"))
```

Length - feeding rate relationships from personal data:  
$$fr(Antigua, S. viride, i) = 445-8*L$$
$$fr(Antigua, S. vetula, i) = 1030-12*L$$
$$fr(Bonaire, S. viride, i) = 1057-17*L$$
$$fr(Bonaire, S. vetula, i) = 1347+10*L$$

Feeding rates as published by Bruggemann/Bozec
$$fr(Published, S. viride, i) = 1089-17*L-56 $$
$$fr(Published, S. vetula, initial) = 3329-33*L$$

Bite sizes as predicted by Bruggemann/Bozec:
$$bs(S. vetula) = 4.013*10^{-4}*L^2$$
$$bs(S. viride) = 5.257*10^{-4}*L^2$$

```{r, echo=F, message=F, warning=F}
knitr::include_graphics(here("figs/areagrazed.png"))
```

@@

```{r, echo=F, message=F, warning=F}
knitr::include_graphics(here("figs/pca_bent.png"))
```

>>>>

---
title: "Manuscript draft"
author: "Molly Wilson"
date: "Dec. 2018"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
---

@@

sum_id_pca <- read.csv(here("data","sum_id_pca.csv"), stringsAsFactors=F) %>%
  select(-X) %>% na.omit()
sum_ssp_pca <- read.csv(here("data","sum_ssp_pca.csv"), stringsAsFactors=F) %>%
  select(-X) %>% na.omit()
```

@@

## Data collection
* Sites (13, map), timeline
* Fish and benthic community data
* Behavioral data:
    - Species: *Sparisoma viride* and *Scarus vetula*, initial and terminal phase greater than 15cm
    - 2 minute follows, calibration period, outside of previously established FID
    - Recording time budgets as well as bite rates during grazing forays (define)
    - Discarded data of incomplete follows or where fish were visably disturbed/fled
    - Timing of data collection distributed throughout day

@@

## Biplots
```{r, echo=F, message=F, warning=F}
knitr::include_graphics(here("figs/pca_pred.png"))
```

@@

```{r, echo=F, message=F, warning=F}
knitr::include_graphics(here("figs/pca_pred.png"))
```
